---
title: "Week3 Assignment"
author: "James Kuruvilla"
date: "September 11, 2017"
output: html_document
---


#### 3. Copy The introductory example. The vector 'name' stores the  extracted names
**a. Use the tools of this chapter to rearrange the vector so that all elements conform to the standard first_name last_name.**

```{r setup, include=TRUE}
library(stringr)

raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

name<-unlist(str_extract_all(raw.data,"[[:alpha:], . ]{2,}"))
name

#Remove Titles like Rev, Dr. Mr. etc
full_names <- str_replace(name, pattern = "Rev. |Dr. |Mr. ", replacement = ""); 

#Define Data Frame and the varibles
# ================================
df = data.frame(First_Name = character(), Last_Name = character())
First_Name <- character(length(full_names))
Last_Name <- character(length(full_names))
# ================================

for (i in 1:length(full_names))

  {
   if (str_detect(full_names[i],",")) #if there is a coma in the name, reverse the order
     {
         Last_Name[i] <- str_extract(full_names[i], "[[:alpha:]+]{2,}")
         # Take the name after the space
         First_Name[i] <- str_trim(str_extract(full_names[i], "[[:space:]][[:alpha:]+]{2,}"))
         # Concatenate in reverse order
         full_names[i] <- str_c(First_Name[i],Last_Name[i],sep=" ")
     }
  else 
     {
       First_Name[i] <- str_extract(full_names[i], "[[:alpha:]+]{2,}")
       Last_Name[i] <- str_trim(str_extract(full_names[i], "[[:space:]][[:alpha:]+]{2,}")) # Take the name after the space
     }
 }
full_names
df <- data.frame(First_Name,Last_Name,stringsAsFactors = FALSE)
df

```
**b. Construct Logical vector indicating whether a character has a title (i.e. Rev. and Dr.)**


```{r}
logi_vec<-str_detect(name,"[[:alpha:]+]{2,3}[.]")

logi_vec
```




**c. Construct Logical vector indicating whether a character has a second name**

```{r}
logi_vec_sn <- str_detect(name, "[[:upper:]]\\.")

logi_vec_sn

```

#### 4. Describe the type of strings that conform  to the following regular expressions and construct an example that is matched by the regular expression

**a. [0-9]+\\$**

This will find the match for a string consists of ONLY digits from 0 to 9 and ends with a $ sign 

Ex: 
```{r}
s <- "This is a sample string with 81292323$ and 9823429 for testing"
str_extract(s,"[0-9]+\\$")

```

**b. \\b[a-z]{1,4}\\b**

This is to find a matching string consists of between 1 and 4 lowercase letters and its between 2 word edges. 

```{r}
s1 <- "This sentence is a set of words to be tested. All the words consists of 4 or less Lower case letters will be selected"

str_extract_all(s1,"\\b[a-z]{1,4}\\b")

```
**c. .*?\\.txt$**

This expression will find a matching string whih ends with .txt but before that is optional.

```{r}
tst <- c("kljsdfa.txt$","askd.txt",".txt", "aslkdjatxt","sdasd.txtasd")

unlist(str_extract_all(tst,".*?\\.txt$"))

```

**d. \\d{2}/\\d{2}/\\d{4}**  

This will search and return a string with 2 digits then '/' another 2 digits the '/' and then 4 digits. like (dd/dd/dddd)

```{r}

dt <- "The birth date of Mr.E is 02/29/2000. So every year that is Celebrated on 02/28th."

str_extract_all(dt,"\\d{2}/\\d{2}/\\d{4}")


```

**e. <(.+?)>.+?</\\1>**  
This is like html tags. This means a string that cantains two pairs of angle brakets with one backreference. Inside the pair of angle brackets, there must be some characters. 

```{r}

txt <- c("<head>hello</head>", "<body>world</body>", "<>notgood<>")

unlist(str_extract_all(txt, "<(.+?)>.+?</\\1>"))

```

### 9. The following code hides a secret message. Crack it with R and regular expressions. Hint: Some of the characters are more revealing than others! The code snippet is also available in the materials at www.r-datacollection.com.


"clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5 fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

```{r}
cd <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5 fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

code<-unlist(str_extract_all(cd,"[[:upper:].]{1,}"))

code <- paste(code, collapse = "")

code <- str_replace_all(code, pattern = "\\.", replacement = " ")

code
```

